Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-04-20 main.tex
:lock: Rank relaxation proof

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $\boldsymbol{0}$ denotes zero vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $j$ denotes the imaginary unit. $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denotes the subspace spanned respectively by real and complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector as the main diagonal of the input matrix. $\boldsymbol{x} \succeq \boldsymbol{0}$ means every element of $\boldsymbol{x}$ is nonnegative, and $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation with respect to random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ denote respectively the stationary value and the value at iteration $i$.
		\end{subsection}
	\end{section}

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{\lvert{\phi_l}\rvert=1, \quad l=1,\dots,L}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}

@@

			Plugging \eqref{eq:taylor_1} -- \eqref{eq:taylor_3} into \eqref{eq:z_irs}, we obtain the DC current approximation \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
			\begin{figure*}[!b]
				\hrule
				\begin{align}
					\tilde{z}(\boldsymbol{\Phi}^{(i)})
					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 \Re\left\{t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right).\label{eq:z_irs_approx}
				\end{align}
			\end{figure*}
			\begin{maxi!}
				{\boldsymbol{\Phi}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
				\addConstraint{\boldsymbol{\Phi}_{l',l'}=1, \quad l'=1,\dots,L+1}\label{co:irs_modulus}
				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}
			\end{maxi!}
			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:z_irs_approx}. Since the remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank}, we apply the rank relaxation technique that is widely adopted in SDP to formulate a convex problem~\eqref{ob:irs} -- \eqref{co:irs_sd}. The tightness of rank relaxation is verified below.

			\begin{proposition}\label{pr:relaxation}
				Any solution $\boldsymbol{\Phi}$ to the relaxed passive beamforming problem~\eqref{ob:irs} -- \eqref{co:irs_sd} satisfies $\mathrm{rank}(\boldsymbol{\Phi})=1$ such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
			\end{proposition}

@@

		\begin{subsection}{Low-Complexity Adaptive Design}
			The GP Algorithm~\ref{al:gp} achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}. To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF under TS and PS setups. The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
			\end{equation}
			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity. In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session and multisine amplitude \eqref{eq:smf} is used in the energy session. In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha \label{eq:s_p}
			\end{align}

@@

	\begin{appendix}
		\begin{subsection}{Proof of Proposition~\ref{pr:relaxation}}\label{ap:relaxation}
			Problem~\eqref{op:irs} after rank constraint relaxation is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, hence strong duality holds and the duality gap is zero. The Lagrangian function of problem \eqref{ob:irs} -- \eqref{co:irs_sd} at iteration $i$ is given by equation \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_rate}, \eqref{co:irs_modulus} and \eqref{co:irs_sd}. $\zeta$ collects all constant terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
			\begin{figure*}[!b]
				\hrule
				\begin{align}\label{eq:lagrangian}
					\mathcal{L}
					&= - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
						\Bigr) - \frac{3}{8} \beta_4 \rho^2 \Biggl(
							4 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
								\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
							\Bigr) + \sum_{k=-N+1}^{N-1} 2 \Re\Bigl\{
								(t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
									\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
								\Bigr)
							\Bigr\}\nonumber\\
					&\quad+ 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
							\Bigr) - \mathrm{tr}^2 \Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
							\Bigr)
						\Biggr)\nonumber + \mu \Biggl(
						2^{\bar{R}} - \prod_{n=1}^N \biggl(
							1 + \frac{(1-\rho) \mathrm{tr}\Bigl(
								\boldsymbol{C}_n \boldsymbol{\Phi}^{(i)}
							\Bigr)}{\sigma_n^2}
						\biggr)
					\Biggr)\nonumber\\
					&\quad+ \mathrm{tr}\biggl(
						\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
							\boldsymbol{\Phi}^{(i)} \odot \boldsymbol{I} - \boldsymbol{I}
						\Bigr)
					\biggr) - \mathrm{tr} \Bigl(
						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
					\Bigr) + \zeta
				\end{align}
			\end{figure*}
			The corresponding Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions can be expressed as

			\begin{subequations}
				\begin{equation}\label{eq:lagrange_multiplier}
					\mu^\star \ge 0, \boldsymbol{\nu}^\star \succeq \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:complementary_slackness}
					\boldsymbol{\nu}^\star \odot \mathrm{diag}^{-1}(\boldsymbol{\Phi}^\star) = \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \boldsymbol{\Phi}^\star = \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:gradient}
					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
				\end{equation}
			\end{subequations}

		\end{subsection}

>>>>

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denotes the subspace spanned respectively by real and complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector that retrieves the main diagonal of the input matrix. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation with respect to random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ denote respectively the stationary value and the value at iteration $i$.
		\end{subsection}
	\end{section}

@@

	\begin{section}{Problem Formulation}\label{se:problem_formulation}
		We characterize each R-E boundary point through a current maximization problem subject to sum rate, transmit power, and IRS magnitude constraints as
		\begin{maxi!}
			{\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho}{z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)}{\label{op:original}}{\label{ob:original}}
			\addConstraint{R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) \ge \bar{R}}\label{co:original_rate}
			\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{w}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{w}_{\mathrm{P}}}\rVert^2\right)\le{P}}\label{co:original_power}
			\addConstraint{\lvert{\boldsymbol{\phi}}\rvert=\boldsymbol{1}}\label{co:original_modulus}
			\addConstraint{0 \le \rho \le 1.}
		\end{maxi!}

@@

			Since $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices, $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real and we have

			\begin{equation}\label{eq:coupled_terms}
				\sum_{k=-N+1}^{N-1} \Re\left\{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*\right\} = \sum_{k=-N+1}^{N-1} 2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^*
			\end{equation}

			Plugging \eqref{eq:taylor_1} -- \eqref{eq:coupled_terms} into \eqref{eq:z_irs}, we obtain the DC current approximation \eqref{eq:z_irs_approx} and transform problem~\eqref{op:original} to
			\begin{figure*}[!b]
				\hrule
				\begin{align}
					\tilde{z}(\boldsymbol{\Phi}^{(i)})
					& = \frac{1}{2}{\beta_2}{\rho}(t_{\mathrm{I},0}^{(i)}+t_{\mathrm{P},0}^{(i)}) + \frac{3}{8}{\beta_4}{\rho^2} \left(4 t_{\mathrm{I},0}^{(i)}t_{\mathrm{I},0}^{(i-1)} - 2 (t_{\mathrm{I},0}^{(i-1)})^2 + \sum_{k=-N+1}^{N-1}{2 t_{\mathrm{P},k}^{(i)} (t_{\mathrm{P},k}^{(i-1)})^* - t_{\mathrm{P},k}^{(i-1)} (t_{\mathrm{P},k}^{(i-1)})^*}\right)\nonumber\\
					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left(\frac{1}{2}(t_{\mathrm{I},0}^{(i)} + t_{\mathrm{P},0}^{(i)})(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) - \frac{1}{4}(t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)})^2 - \frac{1}{4}(t_{\mathrm{I},0}^{(i)} - t_{\mathrm{P},0}^{(i)})^2\right).\label{eq:z_irs_approx}
				\end{align}
			\end{figure*}
			\begin{maxi!}
				{\boldsymbol{\Phi}}{\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs}}{\label{ob:irs}}
				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_rate}
				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_modulus}
				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_sd}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}
			\end{maxi!}
			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:z_irs_approx}. Since the remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank}, we apply the rank relaxation technique that is widely adopted in SDP \cite{Luo2010a} to formulate a convex problem~\eqref{ob:irs} -- \eqref{co:irs_sd}. The tightness of rank relaxation is verified below.

			\begin{proposition}\label{pr:relaxation}
				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs} -- \eqref{co:irs_sd} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$ such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
			\end{proposition}

@@

		\begin{subsection}{Low-Complexity Adaptive Design}
			The GP Algorithm~\ref{al:gp} achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}. To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF under TS and PS setups. The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
			\end{equation}
			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity. In the low-complexity TS waveform scheme, modulated amplitude \eqref{eq:wf} is used in the data session and multisine amplitude \eqref{eq:smf} is used in the energy session. In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and choose the modulated and multisine amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
			\end{align}

@@

	\begin{appendix}
		\begin{subsection}{Proof of Proposition~\ref{pr:relaxation}}\label{ap:relaxation}
			For any feasible $\boldsymbol{\Phi}$ to problem~\eqref{op:irs}, $\mathrm{tr}(\boldsymbol{\Phi})=L+1$ always hold due to the modulus constraint~\eqref{co:irs_modulus}. Therefore, we add a constant term $-\mathrm{tr}(\boldsymbol{\Phi})$ to \eqref{ob:irs} and formulate an equivalent problem as
			\begin{maxi!}
				{\boldsymbol{\Phi}}{-\mathrm{tr}(\boldsymbol{\Phi})+\tilde{z}(\boldsymbol{\Phi})}{\label{op:irs_equivalent}}{\label{ob:irs_equivalent}}
				\addConstraint{R(\boldsymbol{\Phi}) \ge \bar{R}}\label{co:irs_equivalent_rate}
				\addConstraint{\mathrm{diag}^{-1}(\boldsymbol{\Phi})=\boldsymbol{1}}\label{co:irs_equivalent_modulus}
				\addConstraint{\boldsymbol{\Phi}\succeq{\boldsymbol{0}}}\label{co:irs_equivalent_sd}
				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_equivalent_rank}}
			\end{maxi!}

			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent} -- \eqref{co:irs_equivalent_sd} is convex with respect to $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds. The corresponding Lagrangian function at iteration $i$ is given by equation \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
			\begin{figure*}[!b]
				\hrule
				\begin{flalign}\label{eq:lagrangian}
					\mathcal{L}
					&= \mathrm{tr}\left(\boldsymbol{\Phi}^{(i)}\right) - \frac{1}{2} \beta_2 \rho \mathrm{tr}\Bigl(
							(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
						\Bigr) - \frac{3}{8} \beta_4 \rho^2 \Biggl(
							4 t_{\mathrm{I},0}^{(i-1)} \mathrm{tr}\Bigl(
								\boldsymbol{C}_{\mathrm{I},0} \boldsymbol{\Phi}^{(i)}
							\Bigr) + \sum_{k=-N+1}^{N-1} 2 (t_{\mathrm{P},k}^{(i-1)})^* \mathrm{tr}\Bigl(
								\boldsymbol{C}_{\mathrm{P},k} \boldsymbol{\Phi}^{(i)}
							\Bigr)
							&&\nonumber\\
					&\quad+ 2 (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) \mathrm{tr}\Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
							\Bigr) - \mathrm{tr}^2 \Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^{(i)}
							\Bigr)
						\Biggr) + \mu \Biggl(
						2^{\bar{R}} - \prod_{n=1}^N \biggl(
							1 + \frac{(1-\rho) \mathrm{tr}\Bigl(
								\boldsymbol{C}_n \boldsymbol{\Phi}^{(i)}
							\Bigr)}{\sigma_n^2}
						\biggr)
					\Biggr)&&\nonumber\\
					&\quad+ \mathrm{tr}\biggl(
						\mathrm{diag}(\boldsymbol{\nu}) \odot \Bigl(
							\boldsymbol{\Phi}^{(i)} \odot \boldsymbol{I} - \boldsymbol{I}
						\Bigr)
					\biggr) - \mathrm{tr} \Bigl(
						\boldsymbol{\Upsilon} \boldsymbol{\Phi}^{(i)}
					\Bigr) + \zeta,&&
				\end{flalign}
			\end{figure*}
			The Karush–Kuhn–Tucker (KKT) conditions on the primal and dual solutions are
			\begin{subequations}
				\begin{equation}\label{eq:lagrange_multiplier}
					\mu^\star \ge 0, \boldsymbol{\Upsilon}^\star \succeq \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:complementary_slackness}
					\boldsymbol{\nu}^\star \odot \mathrm{diag}^{-1}(\boldsymbol{\Phi}^\star) = \boldsymbol{0}, \boldsymbol{\Upsilon}^\star \boldsymbol{\Phi}^\star = \boldsymbol{0},
				\end{equation}
				\begin{equation}\label{eq:gradient}
					\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L} = 0.
				\end{equation}
			\end{subequations}

			We derive the gradient explicitly and rewrite \eqref{eq:gradient} as
			\begin{equation}
				\boldsymbol{\Upsilon}^\star = \boldsymbol{I} - \boldsymbol{\Delta}^\star
			\end{equation}
			where $\boldsymbol{\Delta}^\star$ is defied in \eqref{eq:delta}.
			\begin{figure*}[!b]
				\begin{flalign}\label{eq:delta}
					\boldsymbol{\Delta}^\star
					&= \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) + \frac{3}{4} \beta_4 \rho^2
						\Biggl(
							2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
					&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
								(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
							\Bigr)
						\Biggr) + \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
						1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
							\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
						\Bigr)}{\sigma_{n'}^2}
					\Biggr) - \mathrm{diag}(\boldsymbol{\nu^\star}).&&
				\end{flalign}
			\end{figure*}
			Note that \eqref{eq:complementary_slackness} suggests $\mathrm{rank}(\boldsymbol{\Upsilon}^\star)+\mathrm{rank}(\boldsymbol{\Phi}^\star) \le L+1$. By reusing the proof in Appendix A of \cite{Xu2020}, we conclude $\mathrm{rank}(\boldsymbol{\Upsilon}^\star) \ge L$. On the other hand, $\boldsymbol{\Phi}^\star$ cannot be zero matrix and $\mathrm{rank}(\boldsymbol{\Phi}^\star) \ge 1$. Therefore, any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed problem~\eqref{op:irs_equivalent} satisfies $\mathrm{rank}(\boldsymbol{\Phi}^\star)=1$. Due to the equivalence between \eqref{ob:irs} and \eqref{ob:irs_equivalent}, $\boldsymbol{\Phi}^\star$ is also optimal to the relaxed problem~\eqref{op:irs} and Proposition~\ref{pr:relaxation} holds.
			% \begin{figure*}[!b]
			% 	\begin{flalign}\label{eq:lagrangian_gradient}
			% 		\nabla_{\boldsymbol{\Phi}^\star} \mathcal{L}
			% 		&= \boldsymbol{I} - \frac{1}{2} \beta_2 \rho (\boldsymbol{C}_{\mathrm{I},0}+\boldsymbol{C}_{\mathrm{P},0}) - \frac{3}{4} \beta_4 \rho^2
			% 			\Biggl(
			% 				2 t_{\mathrm{I},0}^{(i-1)} \boldsymbol{C}_{\mathrm{I},0} + \sum_{k=-N+1}^{N-1} (t_{\mathrm{P},k}^{(i-1)})^* \boldsymbol{C}_{\mathrm{P},k} + (t_{\mathrm{I},0}^{(i-1)} + t_{\mathrm{P},0}^{(i-1)}) (\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0})&&\nonumber\\
			% 		&\quad- (\boldsymbol{C}_{\mathrm{I},0} - \boldsymbol{C}_{\mathrm{P},0}) \mathrm{tr}\Bigl(
			% 					(\boldsymbol{C}_{\mathrm{I},0} + \boldsymbol{C}_{\mathrm{P},0}) \boldsymbol{\Phi}^\star
			% 				\Bigr)
			% 			\Biggr) - \mu^\star \sum_{n=1}^N \frac{(1-\rho) \boldsymbol{C}_n}{\sigma_n^2} \prod_{n'=1,n' \ne n}^N \Biggl(
			% 			1 + \frac{(1-\rho)\mathrm{tr}\Bigl(
			% 				\boldsymbol{C}_{n'} \boldsymbol{\Phi}^\star
			% 			\Bigr)}{\sigma_{n'}^2}
			% 		\Biggr)&&\nonumber\\
			% 		&\quad+ \mathrm{diag}(\boldsymbol{\nu^\star}) - \boldsymbol{\Upsilon}^\star.&&
			% 	\end{flalign}
			% \end{figure*}
		\end{subsection}
